Medical Concept Extraction

### 2012-12-17 paper/paper.tex
Adding rows to results.
more discussion bs

After extensive testing of various subsets from our initial feature set, we decided to include all of the features discussed in Section 4.2 as the complete sent proved to be optimal for classification performance. Certain features (metric units, word endings, prognosis locations, and flag words as discussed in Section 4.2.7) were eliminated before significant testing was performed as their proved to have an appreciable negative impact on our F1 scores when testing toy examples.

>>>>

After extensive testing of various subsets from our initial feature set, we decided to include all of the features discussed in Section 4.2 as the complete set proved to be optimal for classification performance. Certain features (metric units, word endings, prognosis locations, and flag words as discussed in Section 4.2.7) were eliminated before significant testing was performed as they proved to have an appreciable negative impact on our F1 scores when testing toy examples.

Our more extensive tests also revealed that our baseline F1 score is primarily a reflection of the inclusion of a single feature: the word itself.  In that sense, much of our performance can be credited purely to machine learning with one particularly strong feature. However, our additional improvements on this score required more in-depth linguistic analysis of our training data. Moreover, all of our machine learning algorithms showed comparable improvements with more language-driven features--these features show a measure of success that is independent from the chosen canned classifier. Nevertheless, we can always argue for a more eloquent implementation of our system in spite of our successful results.
